A 3D curvilinear skeletonization algorithm with application to path tracing

### 2012-12-04 reviews/answer_to_reviewers.tex

\documentclass[final,envcountsame]{article}

\usepackage[margin=1.2in]{geometry}

\begin{document}

\title{Answers to the reviewers}
\author{John Chaussard \and Laurent No\"{e}l \and Venceslas Biri \and Michel Couprie}
\maketitle

We would like to thank the reviewers for their time and for all the constructive feedback they provided us.

\section{Answer to reviewer 1}

\begin{itemize}

\item p. 3, §2: I do not know if the notation $X^{­}$ is often used but I feel this may be a bad choice: suggesting that maybe a $X^{+}$ also exists.. Why not use $\widehat{X}$ which will easily recall the corresponding $\hat{f}$ notation?

\textit{Done. We also changed the sign for the complement, which was $\overline{X}$, to $X^c$, in order to make sure the reader will not mistake the overline symbol with the widehat.} \\

\item p. 5 and 8: why did you numbered the first line of each algorithm "2" instead of "1"?!

\textit{This was not made on purpose, and was due to the deprecated \textbackslash lnl tag used to label lines in the algorithm in order to refer to them later. Using \textbackslash label tag instead solved the problem.} \\

\item p. 6, section 4.2, §2: I was not able to figure how two *different* points in $Z^n$ may have an Euclidean distance strictly lower than 1. Did you meant "is equal to 1" instead of "is equal or inferior to 1"? (I assume this was only because the common sentence is "is equal of inferior to a distance $n>1$")

\textit{This was made in order to include the point itself in the set of its direct neighbours. As this is unnecessary, we changed the definition of 1-neighbours to points having an euclidean distance equal to 1. However, we finally decided to remove this part and directly refer to $L_1$ distance, as reviewer 2 suggested.} \\

\item p. 7, end of the same sentence: ".. the radius of the largest maximal 1­ball contained in $S$ and containing $x$.": I see no reason for this maximal ball to be unique. The maximal radius is obviously unique, but many equivalent maximal balls of this radius may cover $x$, isn't it?

\textit{This is right, and it has been corrected in the new version.} \\

\item \begin{itemize}
\item p. 1, in the abstract, "These skeletons are used * a new path tracing": I suppose "in" is missing here. 
\item p. 1, §2, "To avoid the noise resulting..". I suggest to replace "avoid" by "reduce" since, as far as I know, nobody knows a magical method enabling to avoid any error in such a context! 
\item p. 1, §3, "If a ray.. its contribution is * null.": I suggest "is considered null" or "is set to null" since this is not physically correct but practically mandatory. 
\item p. 2, section 2 and further: I would spell "3d" as "3D". 
\item p. 3, §2: I would have defined $F^n_m$ first and $F^n$ just after as the union of $F^n_m$ for all $m$. Defining $F^n$ as "the set of all faces" (without specifically spelling it as "m­faces") may confuse the reader and let him believe that only 2­faces (what is most of the time named "faces") are concerned. 
\item p. 3, §6, "To transpose such *an* image *$S$* to the cubical complex.." 
\item p. 5, last §, "two previously listed strategies: *it* finds": "it" instead of "its". 
\item p. 5, same sentence: "..to decide *whether* to preserve them, or not, in the result." 
\item p. 7, §1: The maximal 1­ball *of* $S$..": I suggest to replace "of" by "in". 
\end{itemize}

\textit{Done.} \\

\end{itemize}

\section{Answer to reviewer 2}

\begin{itemize}

\item The discussion in Section 5.2 assumes some things. For example, if there are different sources of light and the image is quite symmetric, it may easily happen that $imp_n=n$. In this case the discussion does not go through.
Also, I get the feeling that the presentation is tailored to ONE light source. It would be better to make clear in the discussion that the method works for several light­sources.

\textit{If there are multiple light sources in the scene, the one closest to $n$ is chosen in order to computer $imp_n$, therefore, we cannot have both points equal. If $n$ is equidistant to two light sources, then (in the current algorithm's version), we choose randomly one light source.
We added the strategy about multiple light sources at the end of section 5.2, just before the "sampling according to L" paragraph.}

\item In the experiments, there is a significant speed up in most cases, but in Sponza 2. Is there any explanation for this difference in the behavior of the speed up?

\textit{For Sponza 2, some speckles appear in the resulting image. Because of these "extreme pixels", our algorithm takes more time to get close enough to the required MSE. We are currently investigating the source of these speckles, and how to reduce them. Unfortunately, the page restriction set for the DGCI article does not allow us to discuss this matter in the paper.}\\

\item Why do not define d(x,y) as the $L_1$ ­distance instead of using a graph­based distance?

\textit{We changed the way we introduce, in section 4.2, the distance d, and now rely on the well-known definition of the L1 distance}.\\

\item Why do you call the skeleton curvilinear? What is curvilinear about it?

\textit{The skeleton is called curvilinear because the skeletonization algorithm preserves, in the visual aspect preservation step, only edges. Surfaces may appear if the topology of the object requires it : in this case, these surfaces were not preserved for geometrical reasons, but for topological reasons. Surfacic skeletons also exist : in this case, surfaces may be preserved during the visual aspect preservation step. Our algorithm is a curvilinear skeletonization algorithm.
We explained why this terminology choice in the article, at the end of section 4.3.}\\

\item Do not use $d$ in definition 7 because $d$ is already used in the Algorithm. (It is confusing.)

\textit{Done. We use delta instead.}\\

\item I do not understand the 3rd paragraph of Section 4.

\textit{The skeleton obtained using Alg. 1 could end up being too much reduced, as Alg. 1 does not preserve the visual aspect of the object during thinning. For example, the skeleton of a corridor could end up being reduced to a single vertex. We changed this part in order to make this point clearer.}\\

\item The path­tracing algorithm is quite standard and I assume that it appears in textbooks of Comp Graphics. I would suggest referring to one such book (perhaps instead of [8], but both references would also be ok.).

\textit{We keep reference [8] as it is widely used articles about path tracing. Although another reference, such as the one suggested, would be very interesting, the page limitation do not allow us to add a single reference.}

\item \begin{itemize}

\item page 3, line 8: ")" is missing.
\item Def 3: "Let Y..., the complex X collapses....". These are two different sentences and there should be a period between them, not a comma.
\item "elements [whose ...] is interesting"

\end{itemize}

\textit{Done.}

\end{itemize}

\section{Answer to reviewer 3}

\begin{itemize}

\item \begin{itemize}
\item Abstract, l. 4: used in a new path tracing algorithm
\item p. 3, l.1: Cartesian
\item Algorithm 1: for $t=1­­>n$ do
\item p. 5 l. ­3: it finds
\item p. 7 l. 11: with regard. l.17: example; 
\item in Fig. 3. l. ­1: In the same way
\item p. 9 : at point x; at x
\item p. 10: l. 5 gives. l. 19: don't­­ $>$ do not. l. ­18: preprocessing performed on it. 
\end{itemize}

\textit{Done.}\\

\end{itemize}

\end{document}

### 2012-12-04 application_to_path_tracing.tex
Re commit

In this section, we explain how to use the curvilinear skeleton of the voids of the scene in order to enhance the path tracing algorithm. We start by defining some basic elements related to path tracing and we present our skeleton based path tracing algorithm.

@@

Let $O$ be the origin of the camera in the scene. For each pixel $P$ of the final image, let $x$ be the nearest intersection point of the ray $(O, \overrightarrow{OP} = -\Theta)$ with an element of the scene. To obtain the luminosity, we must solve the rendering equation \cite{Ka86} which is a recursive integral equation, the integrand containing the radiance function that we must compute:

\begin{align*}
L(x \rightarrow \Theta) &= L_e(x \rightarrow \Theta) + \int_{\Phi \in \Omega_x} f_s(x, \Theta \leftrightarrow \Phi) L(r(x, \Phi) \rightarrow -\Phi) d\omega_\Phi
\end{align*}

$L$ is the radiance (a radiometric quantity that represents luminosity) from point $x$ toward direction $\Theta$ and $L_e$ is the emitted radiance (non null only on light sources). The point $r(x, \Phi)$ is the nearest visible point from $x$ in the direction $\Phi$ of the hemisphere $\Omega_x$. The $f_s$ function expresses how much luminosity is exchanged, on point $x$, between an incoming ray $\Phi$ and the outgoing ray $\Theta$. It represents the material properties of the surface at $x$.

@@

The function $p$ is a probability density function (pdf) that is used to sample $\Phi$. This estimator is unbiased, meaning that the expected value $E[\langle L_r(x \rightarrow \Theta) \rangle]$ is equal to $L_r(x \rightarrow \Theta)$. The variance of the estimator expresses its quality and depends on the choosen pdf $p$. The best choice is a pdf that matches the shape of the function to integrate (ie. gives high density to samples that have high values for the function and low density to samples that have low values).
The strategy of choosing an adapted pdf is called \myem{importance sampling}~\cite{Ka86} and is used in global illumination to improve the convergence speed of the algorithms.

The algorithm computes $L$ as follow: first, it chooses one random direction $\Phi$ based on the pdf $p$. Then, it applies the estimator by calling $L$ recursively to compute $L_r$ (shoots a new ray in the direction $\Phi$, computes the new hit point with the scene, and compute the new radiance at this point). Finally, it returns the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops when either a maximal number of bounces or a directly illuminated area have been reached.

@@

As stated in the introduction, a curvilinear skeleton of the void (with some preprocessing performed on it) gives us information on which directions the light comes from. Given these directions, we can build a efficient pdf $p_{skel}$ and guide our rays by sampling the hemispheres with $p_{skel}$.

The integrand of $L_r$ is:

@@

The most common strategy used to sample $\Omega_x$ is to use the function $f_s$ because it is an input of the algorithm.
The term $L$, which represents the distribution of light in the scene, is unknown. Our method gives a way to sample $L$.

@@

Let $n$ be a node of the skeleton and $V_n$ the set of visible nodes from $n$ along the shortest path toward $n_L$. The importance point $imp_n$ associated to $n$ is the barycenter of $V_n$. An example is shown on Fig.~\ref{fig::example_imp} on the left.

The algorithm can be extended to multiple light sources by taking into account, for each node, only the closest light source when following the curvilinear skeleton path.

\begin{figure}[tb]
\begin{center}
\begin{tabular}{l|r}
	\myincludegraphics{0.3\textwidth}{graph_heuristic.pdf} ~~~~~~&
	~~~~~~ \myincludegraphics{0.6\textwidth}{skel.jpg} \\
\end{tabular}
\caption[Example of importance point construction]{\label{fig::example_imp} \textbf{On the left}, we illustrate the importance point $imp_n$ associated to a node $n$. The dotted black line shows the closest node to $n$ not included in $V_n$. \textbf{On the right}, an example of the curvilinear skeleton (in red) obtained in the Sponza scene.}
\end{center}
\end{figure}

@@

Given a point $x$ on the scene and a direction $\Theta$, we want to compute $L(x \rightarrow \Theta)$ and then sample the hemisphere $\Omega_x$. We search for the nearest skeleton node $n$ to $x$ and its importance point $imp_n$. We sample the hemisphere with a power-cosine pdf centered on $\overrightarrow{x\,imp_n}$:
\begin{equation*}
p_{skel}(\Phi) = \frac{s + 1}{2\pi} cos^s \alpha
\end{equation*}
with $\alpha$ the angle between $\overrightarrow{x\,imp_n}$ and $\Phi$, $s$ being a parameter called skeleton strength. The higher $s$ is, the closer to $\overrightarrow{x\,imp_n}$ we sample.

@@

\begin{figure}[tbhp]
\begin{center}
\includegraphics[scale=0.17]{images/four_scenes_for_dgci.png}
\caption{\label{fig:results}Same scene rendered using the classical path tracing (image $a$) or our method (image $b$). Images $c$ and $d$ are both details of respectively images $a$ and $b$ }
\end{center}
\end{figure}

>>>>

In this section, we explain how the curvilinear skeleton of the voids of the scene can enhance the path tracing algorithm. We start with some basic elements related to path tracing and then present our modified path tracing algorithm.

@@

Let $O$ be the origin of the camera in the scene. For each pixel $P$ of the final image, let $x$ be the nearest intersection point of the ray $(O, \overrightarrow{OP} = -\Theta)$ with an element of the scene. To obtain the luminosity, we must solve the rendering equation \cite{Ka86} which is a recursive integral equation, the integrand containing the radiance function that we must compute:
\begin{center}
$L(x \rightarrow \Theta) = L_e(x \rightarrow \Theta) + \int_{\Phi \in \Omega_x} f_s(x, \Theta \leftrightarrow \Phi) L(r(x, \Phi) \rightarrow -\Phi) d\omega_\Phi$
\end{center}
where $L$ is the radiance (a radiometric quantity that represents luminosity) from point $x$ toward direction $\Theta$ and $L_e$ is the emitted radiance (non null only on light sources). The point $r(x, \Phi)$ is the nearest visible point from $x$ in the direction $\Phi$ of the hemisphere $\Omega_x$. The $f_s$ function expresses how much luminosity is exchanged, on point $x$, between an incoming ray $\Phi$ and the outgoing ray $\Theta$.

@@

The function $p$ is a probability density function (pdf) that is used to sample $\Phi$. This estimator is unbiased, meaning that the expected value $E[\langle L_r(x \rightarrow \Theta) \rangle]$ is equal to $L_r(x \rightarrow \Theta)$. The variance of the estimator expresses its quality and depends on the chosen pdf $p$. The best choice is a pdf that matches the shape of the function to integrate (ie. gives high density to samples that have high values for the function and low density to samples that have low values).
The strategy of choosing an adapted pdf is called \myem{importance sampling}~\cite{Ka86} and is used in global illumination to improve the convergence speed of the algorithms.

The algorithm computes $L$ as follow: it chooses one random direction $\Phi$ based on the pdf $p$ and applies the estimator by calling $L$ recursively to compute $L_r$ (shoots a new ray in the direction $\Phi$, computes the new hit point with the scene, and compute the new radiance at this point). Finally, it returns the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops when either a maximal number of bounces or a directly illuminated area have been reached.

@@

As stated in the introduction, a curvilinear skeleton of the void (with some preprocessing performed on it) gives us information on which directions the light comes from. Given these directions, we can build a efficient pdf $p_{skel}$ and guide our rays by sampling the hemispheres with $p_{skel}$. The integrand of $L_r$ is:

@@

The most common strategy used to sample $\Omega_x$ is to use the function $f_s$ because it is an input of the algorithm.
The term $L$, representing the distribution of light in the scene, is unknown. Our method gives a way to sample $L$.

@@

Let $n$ be a node of the skeleton and $V_n$ the set of visible nodes from $n$ along the shortest path toward $n_L$. The importance point $imp_n$ associated to $n$ is the barycenter of $V_n$. An example is shown on Fig.~\ref{fig::example_imp} on the left.
The algorithm can be extended to multiple light sources by taking into account, when computing the importance point of a skeleton node, only the closest light source.

@@

Given a point $x$ on the scene and a direction $\Theta$, we want to compute $L(x \rightarrow \Theta)$ and then sample the hemisphere $\Omega_x$. We search for the nearest skeleton node $n$ to $x$ and its importance point $imp_n$. We sample the hemisphere with a power-cosine pdf centered on $\overrightarrow{x\,imp_n}$:
\begin{center}
$p_{skel}(\Phi) = \frac{s + 1}{2\pi}  * cos^s \alpha$
\end{center}
with $\alpha$ the angle between $\overrightarrow{x\,imp_n}$ and $\Phi$, $s$ being a parameter called skeleton strength. The higher $s$ is, the closer to $\overrightarrow{x\,imp_n}$ we sample.

@@

\begin{figure}[t]
\begin{center}
\begin{tabular}{l|r}
	\myincludegraphics{0.3\textwidth}{graph_heuristic.pdf} ~~~~~~&
	~~~~~~ \myincludegraphics{0.6\textwidth}{skel.jpg} \\
\end{tabular}
\caption[Example of importance point construction]{\label{fig::example_imp} \textbf{On the left}, we illustrate the importance point $imp_n$ associated to a node $n$. The dotted black line shows the closest node to $n$ not included in $V_n$. \textbf{On the right}, an example of the curvilinear skeleton (in red) obtained in the Sponza scene.}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.17]{images/four_scenes_for_dgci.png}
\caption{\label{fig:results}Same scene rendered using the classical path tracing (image $a$) or our method (image $b$). Images $c$ and $d$ are both details of respectively images $a$ and $b$ }
\end{center}
\end{figure}

### 2012-12-04 skeleton_and_pathtracing.tex
Re commit

\def\V2C{\Psi}
\def\Nset{\mathbb{N}}
\def\Zset{\Z}
\def\Nset{\mathbb{N}}
\def\Rset{\mathbb{R}}
\def\Z{\mathbb{Z}}
\def\Zhalf{\frac{\mathbb{Z}}{2}}
\def\allfaces#1{\mathbb{F}^{#1}}
\def\subfaces#1#2{\allfaces{#1}_{#2}}
\def\subcomplex#1#2{#1 \preceq #2}
\def\complex#1#2{\subcomplex{#2}{\allfaces{#1}}}
\def\cell#1{\hat{#1}}
\def\cellstrict#1{\hat{#1}^*}
\def\closure#1{\widehat{#1}}
\def\princ#1{#1^+}
\def\mydim#1{\dim(#1)}
\def\type#1{\mbox{\it{}Dir\/}(#1)}
\def\orient#1{\mbox{\it{}Orient\/}(#1)}
\def\border#1{\mbox{\it{}Border\/}(#1)}
\def\suchthat{\;|\;}
\def\inter{\cap}
\def\union{\cup}
\def\dinterval#1#2{\{#1,\ldots,#2\}}
\newcommand{\Compl}[1]{#1^c}
\def\finproof{\square}
\def\Zhalf{\frac{\mathbb{Z}}{2}}
\newcommand{\Card}[1]{|#1|}

@@

\begin{abstract}
We present a novel 3D curvilinear skeletonization algorithm which produces filtered skeletons without needing any user input, thanks to a new parallel algorithm based on the cubical complex framework. These skeletons are used in a new path tracing algorithm in order to produce less noisy images in less time than the classical approach.
\end{abstract}

@@

Algorithm~\ref{algo::pardircollapse_v0} does not necessarily preserve geometrical features of the input object in the resulting skeleton, which end up being a single vertex.

In the following, we introduce a new method in the cubical complex framework, requiring no user input, for obtaining a curvilinear skeleton yielding satisfactory geometrical properties. Our method is based on the two previously listed strategies: it finds, during thinning, elements with a specific neighbourhood configuration, and uses a function on these elements to decide whether to preserve them, or not, in the result.

@@

Although the output of Alg.\ref{algo::3d_curvskel} may contain $2$-faces, the algorithm is said to be a \myem{curvilinear skeletonization} algorithm because it only adds $1$-faces (edges) in the inhibitor set $W$ (used for the visual aspect preservation step) (on line \ref{curvskel:01} of Alg.~\ref{algo::3d_curvskel}).
For the same reason, we say that the output of Alg.~\ref{algo::3d_curvskel} is a \myem{curvilinear skeleton}. In Sec.~\ref{sec::appli_pathtrace}, the outputs of Alg.~\ref{algo::3d_curvskel} were always one dimensional complexes.

@@

\begin{figure}[tb]
\begin{center}
\begin{tabular}{cc|cc}
	\myincludegraphics{0.18\textwidth}{hand2.jpg} &
	\myincludegraphics{0.18\textwidth}{hand_curvskel.jpg} &
	\myincludegraphics{0.24\textwidth}{neptune.jpg} &
	\myincludegraphics{0.24\textwidth}{neptune_curvskel.jpg} \\
\end{tabular}
\caption[Results of algorithm \ref{algo::3d_curvskel}]{\label{fig::result_skel} \textbf{Results of algorithm \ref{algo::3d_curvskel}} for two shapes: a hand (left) and a statue (right). In each pair, the rightmost image represents the skeleton.}
\end{center}
\end{figure}

>>>>

\def\V2C{\Psi}
\def\Nset{\mathbb{N}}
\def\Zset{\Z}
\def\Nset{\mathbb{N}}
\def\Rset{\mathbb{R}}
\def\Z{\mathbb{Z}}
\def\Zhalf{\frac{\mathbb{Z}}{2}}
\def\allfaces#1{\mathbb{F}^{#1}}
\def\subfaces#1#2{\allfaces{#1}_{#2}}
\def\subcomplex#1#2{#1 \preceq #2}
\def\complex#1#2{\subcomplex{#2}{\allfaces{#1}}}
\def\cell#1{\hat{#1}}
\def\cellstrict#1{\cell{#1}^*}
\def\closure#1{\widehat{#1}}
\def\princ#1{\check{#1}}
\def\mydim#1{\dim(#1)}
\def\type#1{\mbox{\it{}Dir\/}(#1)}
\def\orient#1{\mbox{\it{}Orient\/}(#1)}
\def\border#1{\mbox{\it{}Border\/}(#1)}
\def\suchthat{\;|\;}
\def\inter{\cap}
\def\union{\cup}
\def\dinterval#1#2{\{#1,\ldots,#2\}}
\newcommand{\Compl}[1]{#1^c}
\def\finproof{\square}
\def\Zhalf{\frac{\mathbb{Z}}{2}}
\newcommand{\Card}[1]{|#1|}

@@

\begin{abstract}
We present a novel 3D curvilinear skeletonization algorithm which produces filtered skeletons without needing any user input, thanks to a new parallel algorithm based on the cubical complex framework. These skeletons are used in a modified path tracing algorithm in order to produce less noisy images in less time than the classical approach.
\end{abstract}

@@

Algorithm~\ref{algo::pardircollapse_v0} does not necessarily preserve geometrical features of the input object in the resulting skeleton (for example, the skeleton of a corridor could be reduced to a single vertex). In the following, we introduce a new method in the cubical complex framework, requiring no user input, for obtaining a curvilinear skeleton yielding satisfactory geometrical properties. Our method is based on the two previously listed strategies: it finds, during thinning, elements with a specific neighbourhood configuration, and uses a function on these elements to decide whether to preserve them, or not, in the result.

@@

Although the output of Alg.\ref{algo::3d_curvskel} may contain $2$-faces, the algorithm is said to be a \myem{curvilinear skeletonization} algorithm because it only adds $1$-faces (edges) in the inhibitor set $W$ (used for the visual aspect preservation step) (on line \ref{curvskel:01} of Alg.~\ref{algo::3d_curvskel}).
For the same reason, we say that the output of Alg.~\ref{algo::3d_curvskel} is a \myem{curvilinear skeleton}. In the scenes studied in Sec.~\ref{sec::appli_pathtrace}, the outputs of Alg.~\ref{algo::3d_curvskel} were one dimensional complexes.

@@

\begin{figure}[tb]
\begin{center}
\begin{tabular}{cc|cc}
	\myincludegraphics{0.16\textwidth}{hand2.jpg} &
	\myincludegraphics{0.16\textwidth}{hand_curvskel.jpg} &
	\myincludegraphics{0.21\textwidth}{neptune.jpg} &
	\myincludegraphics{0.21\textwidth}{neptune_curvskel.jpg} \\
\end{tabular}
\caption[Results of algorithm \ref{algo::3d_curvskel}]{\label{fig::result_skel} \textbf{Results of algorithm \ref{algo::3d_curvskel}} for two shapes: a hand (left) and a statue (right). In each pair, the rightmost image represents the skeleton.}
\end{center}
\end{figure}
